`phyr`: An R package for model-based phylogenetic analyses

### 2018-11-16 ms.Rmd
Added small blurb about cor_phylo [skip ci]

Two functions (`cor_phy` and `binaryPGLMM`) were included in this group. Both of them were included in the R package `ape` [@ape2018] orginally.

`cor_phy`: ... (Lucas?)

>>>>

Two functions (`cor_phylo` and `binaryPGLMM`) were included in this group. Both of them were included in the R package `ape` [@ape2018] orginally.

The function `cor_phylo` computes Pearson correlation coefficients for multiple continuous
traits that may have phylogenetic signal, allowing users to also specify measurement
error.
The underlying methods were originally developed by @zheng2009new.
We improved speed by writing many of the internal functions in c++,
made the input format more flexible,
fixed a mistake that meant measurement error was not included, and
added two new features: parametric bootstrapping and the ability to use optimizers
from the `nlopt` library [@johnson2014nlopt; @powell2009bobyqa; @nelder1965simplex; @rowan1990functional].
